Multi-level modeling with Openflexo/\FML

### 2022-03-25 3-introduction.tex
change requirements format + macros
typo

Model federation is a multi-model management approach based on the use of
virtual models and loosely coupled links. The models in a federation remain
autonomous and are represented in their original technological spaces whereas
virtual models (also called conceptual models) and links that serve as control
components used to present different views to the users and maintain
synchronization. Our solution is based on the model federation infrastructure.
Concretely, we use Openflexo and its internal Federation Modeling Language
(\FML), a language to create, link and manage virtual models, in order to solve
the MULTI process challenge while the federation feature is used solely so as
to provide tools for the resulting process language. Our solution, which is
fully implemented and executable, meets all the requirements.
%\noteFabien{Le paragraphe qui précède me semble redire des choses de la
%section 2, comment fait-on ?}

>>>>

Model federation is a multi-model management approach based on the use of
virtual models and loosely coupled links. The models in a federation remain
autonomous and are represented in their original technological spaces whereas
virtual models (also called conceptual models) and links serve as control
components used to present different views to the users and maintain
synchronization. Our solution is based on the model federation infrastructure.
Concretely, we use Openflexo and its internal Federation Modeling Language
(\FML), a language to create, link and manage virtual models, in order to solve
the MULTI process challenge while the federation feature is used solely so as
to provide tools for the resulting process language. Our solution, which is
fully implemented and executable, meets all the requirements.
%\noteFabien{Le paragraphe qui précède me semble redire des choses de la
%section 2, comment fait-on ?}
